---
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mvnorm Multivariate Normal Distribution}
  %\VignetteEngine{knitr::knit2html(spin(knit = FALSE), force_v1 = TRUE)}
  \usepackage[utf8](inputenc)
---

Multivariate Normal Distribution with Low WAFOM Point Set
---------------------------------------------------------

Calculate Cumulative distribution of Multivariate
Normal Distribution using randomized Quasi-Monte-Calro
Method. Low WAFOM Point Set is used for QMC.

Currently, Low WAFOM Point Set is pre-computed for dimension 4 to 16.
This limitation applies to `mvnorm` function.

Variance-covariance matrix should be diagonally dominant
and, of course, should be symmetric semi-positive definite.

example1:

Simply calculate multivariate normal distribution.
Interval of integration need to be specified by `lower` vector
and `upper` vector. And also `mean` vector and `coval`,
variance-covariance matrix should be given.

```{r}
        library(lwafomps)
        param.s <- 4
        param.lower <- rep(-Inf, param.s)
        param.upper <- rep(0.0, param.s)
        param.mean <- rep(0.0, param.s)
        eps = 0.2 / param.s
        coval<- matrix(eps, nrow=param.s, ncol=param.s)
        d<-diag(1.0 - eps, param.s)
        param.coval <- coval + d
        options(digits=20)
        rs <- mvnorm(lower=param.lower,
                     upper=param.upper,
                     mean=param.mean,
                     coval=param.coval)
        rs
```

example2:

Optional parameter `abseps` specifies expected maximum absolute error.
Absolute error in return value will be less than the value.
Optional parameter `relesp` is usable for relative error.

```{r}
        library(lwafomps)
        param.s <- 4
        param.lower <- rep(-Inf, param.s)
        param.upper <- rep(0.0, param.s)
        param.mean <- rep(0.0, param.s)
        eps = 0.2 / param.s
        coval<- matrix(eps, nrow=param.s, ncol=param.s)
        d<-diag(1.0 - eps, param.s)
        param.coval <- coval + d
        options(digits=20)
        rs <- mvnorm(lower=param.lower,
                     upper=param.upper,
                     mean=param.mean,
                     coval=param.coval,
                     abseps=1.0e-6)
        rs
```

example3:

Optional parameter `probability` is used for specifying a probability
that the true value is in error range. This probability result to
specify error range as sigma, two sigma and three sigma.

```{r}
        library(lwafomps)
        param.s <- 4
        param.lower <- rep(-Inf, param.s)
        param.upper <- rep(0.0, param.s)
        param.mean <- rep(0.0, param.s)
        eps = 0.2 / param.s
        coval<- matrix(eps, nrow=param.s, ncol=param.s)
        d<-diag(1.0 - eps, param.s)
        param.coval <- coval + d
        options(digits=20)
        rs <- mvnorm(lower=param.lower,
                     upper=param.upper,
                     mean=param.mean,
                     coval=param.coval,
                     probability=0.98)
        rs
```
example4:

Optional parameter `tlimit` is used for specifying time limit
by seconds.
Calculation will be stop with some late after time limit.
After time limit, calculated value will be returned, but
it may not satisfy expected error range or probability.

```{r}
        library(lwafomps)
        param.s <- 4
        param.lower <- rep(-Inf, param.s)
        param.upper <- rep(0.0, param.s)
        param.mean <- rep(0.0, param.s)
        eps = 0.2 / param.s
        coval<- matrix(eps, nrow=param.s, ncol=param.s)
        d<-diag(1.0 - eps, param.s)
        param.coval <- coval + d
        options(digits=20)
        rs <- mvnorm(lower=param.lower,
                     upper=param.upper,
                     mean=param.mean,
                     coval=param.coval,
                     probability=0.98,
                     tlimit=1.5)
        rs
```
example5:

Optional parameter parallelism is used for specifying exectuiton block
size.  If your computer has high parallel calculation ability,
specifying large value may improve performance. Calculation is
repeated multiple of parallelism time, too large value will lose
performance.

```{r}
        library(lwafomps)
        param.s <- 4
        param.lower <- rep(-Inf, param.s)
        param.upper <- rep(0.0, param.s)
        param.mean <- rep(0.0, param.s)
        eps = 0.2 / param.s
        coval<- matrix(eps, nrow=param.s, ncol=param.s)
        d<-diag(1.0 - eps, param.s)
        param.coval <- coval + d
        options(digits=20)
        rs <- mvnorm(lower=param.lower,
                     upper=param.upper,
                     mean=param.mean,
                     coval=param.coval,
                     probability=0.98,
                     parallelism=32)
        rs
```
